This is the title [Article v\versionnumber]

### 2022-10-05 manuscript/manuscript.tex
Update 6-dimensional density formula
I think it is incorrect to say that the 6D density g(r,w) is computed
from the individual *voxel* densities g_vox(r) and g_vox(w). Therefore,
I deleted the subscripts.
Update text about different solvents

\begin{equation}
g_\textit{vox} \left( \textbf{r}, \omega \right) \approx g_\textit{vox}(\textbf{r}) g_\textit{vox}(\omega)
\end{equation}

@@

\subsection{GIST with salt-water mixtures}
In \cite{Waibl2021-gist-salt}, an extension of GIST was presented that can use salt-water mixtures as a solvent.
This allows treating salting-out effects, although it was shown that the salting-out coefficient is over-predicted by GIST unless higher-order entropies are incorporated.
Generally, GIST should be able to treat arbitrary solvent mixtures as long as each molecule is sufficiently rigid.

>>>>

\begin{equation}
g_\textit{vox} ( \textbf{r}, \omega ) \approx g(\textbf{r}) g(\omega)
\end{equation}

@@

To run a GIST calculation in a solvent other than water, use the \inlinecode{solute} flag together with a \software{cpptraj} selection mask.
Everything that is not in the \inlinecode{solute} mask is treated as solvent.
If there are multiple solvent species, use the \inlinecode{solventmols} option as described in Section~\ref{sec-salt-water}.
The code will automatically choose three atoms which are used to define the solvent orientation, and print this selection to the output.

Sometimes, \software{cpptraj} does not automatically choose the optimal atoms.
In methanol, for instance, one can either incorporate the C--H bonds or the O--H bond in the selection.
The latter is probably more relevant since it can incorporate hydrogen bonding effects.
Assuming that the alcohol hydrogen is called H1, this could be specified as follows:

\begin{lstlisting}[style=cpptraj]
gist gridcntr <x> <y> <z> \
griddim <Nx> <Ny> <Nz> gridspacn <val> \
solute ^1 rigidatoms O1 H1 C1
\end{lstlisting}

Note that the central atom of the \inlinecode{rigidatoms} selection goes first.

\subsection{GIST with salt-water mixtures}
\label{sec-salt-water}
In \cite{Waibl2021-gist-salt}, an extension of GIST was presented that can use salt-water mixtures as a solvent.
This allows treating salting-out effects, although it was shown that the salting-out coefficient is over-predicted by GIST unless higher-order entropies are incorporated.
Generally, GIST should be able to treat arbitrary solvent mixtures as long as each molecule is sufficiently rigid.
